Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-07-15 MainText.Rmd
writing intro

<!--How copula could be relevent in estimating extreme event's 
influence on extinction risk : introduce Taildep. concept-->
A recent study [@Ghosh_copula] showed the importance, causes 
and consequences of copula structures in associations between ecologically
important variables and demonstrated one example of density-independent metapopulation model where 
copula was used to estimate extinction risk. Copula, a rank based measure, is much more informative 
than linear correlation measure and a widely applied tool in dependence 
modeling [@joe2014_dependence; @nelsen2006_copula]. We will hereby illaborate the idea why
the potential use of copula in modelling extinction risk goes beyond the density-independent model 
and even applicable for a simple age-structured population where its vital rates are influenced by ECEs. 
<!--do I need to explain the details how to make a copula from raw data?-->

>>>>

<!--How copula could be relevent in estimating extreme event's 
influence on extinction risk : introduce Taildep. concept-->
A recent study [@Ghosh_copula] showed the importance, causes 
and consequences of copula structures in associations between ecologically
important variables and demonstrated one example of density-independent metapopulation model where 
copula was used to estimate extinction risk. Copula, a rank based measure of association, is much more informative 
than linear correlation measure and a widely applied tool in dependence 
modeling [@joe2014_dependence; @nelsen2006_copula]. We here introduce the concept of copula in a
manner that follows [@Ghosh_copula]. Copulas separate the information content of a bivariate dataset,
$(x_n, y_n)$ for $n = 1 \ldots N$, into two non-overlapping parts: the information in the marginal 
distributions (which is not about the association between the variables) and the rest of 
the information (which is solely about the association). The association information is revealed by 
the copula plot ($v_n$ against $u_n$) of the raw variables ($y_n$ vs. $x_n$) in Fig...., where 
$u_n$ is the rank of $x_n$ in the set ${x_1, x_2, \ldots , x_n }$, divided by $N + 1$; 
and $v_n$ is the rank of $y_n$ in the set ${y_1, y_2, \ldots , y_n }$, also divided
by $N + 1$. Here the rank of the smallest element of each sets is considered to be 1 and the rank of
the largest element is $N$. We refer to the $u_n$ and $v_n$ as normalized ranks of the $x_n$ and $y_n$. 
Ranking makes the marginal distributions uniform, isolating only the information on 
association between the variables. Here, we will extend the application of copula 
in estimating extinction risk as introduced by [@Ghosh_copula] on why the potential use of copula
in modelling extinction risk goes beyond the density-independent model 
and even applicable for a simple age-structured population where its vital rates are influenced by ECEs.
